\newcommand{\uvec}[1]{\bm{\hat{#1}}}
\newcommand{\bvec}[1]{\bm{\vec{#1}}}

\chapter{Background}
Magnetic resonance imaging is, as the name suggests, enabled by the phenomenon of magnetic resonance.

\section{Origin of MR signal}

\subsection{Nuclear Spins}
Spin is a quantum mechanical property that describes a particle's intrinsic angular momentum. Atoms with an odd
number of protons or neutrons possess net nuclear spin, and therefore have mutually aligned angular momentum $\bvec{S}$
and magnetic dipole moment $\bvec{\mu}= \gamma \bvec{S}$, where $\gamma$ is the gyromagnetic ratio: a known constant
defined for every nucleus. Hydrogen (\ce{^{1}_{1}H}) is such an atom, having one proton and no neutrons. Along a given
axis, hydrogen spins are quantized to $\pm \frac{\hbar}2$.  Therefore, hydrogen dipole moments are likewise quantized to
$\pm \gamma \frac{\hbar}{2}$ (eq. \ref{eq:dipole}).

\begin{equation}\label{eq:dipole}
    \mu = \pm \gamma \frac{\hbar}{2}
\end{equation}

\subsection{Spins in the Presence of External Magnetic Fields}
In the presence of a strong polarizing field pointing in the $\uvec{k}$ direction and with magnitude $B_0$, the
potential energy of a spin with dipole moment $\bvec{\mu}$ is the dot product between the two vectors (eq.
\ref{eq:spin_energy}). Because $\mu$ is quantized, there is a gap $\Delta E$ between realizable energy states (eq.
\ref{eq:delta_E}).

\begin{equation}\label{eq:spin_energy}
    E = - \bvec{\mu} \cdot \bvec{B_0}
\end{equation}

\begin{equation}\label{eq:delta_E}
    \Delta E = \gamma \hbar B_0
\end{equation}

\subsubsection{Polarization}
Spins tend to settle in the low energy state, pointing in the direction of $\bvec{B_0}$. However, at room temperature,
thermal energy vastly exceeds the energy gap between the two states, and the ratio of spins aligned with $\bvec{B_0}$
($n_+$) to those anti aligned ($n_-$) is described by the Boltzmann distribution in eq. \ref{eq:boltzmann}. For hydrogen
($\gamma = \frac{42.58}{2\pi} \frac{MHz}{T}$) at room temperature ($T=273 K$) at a field strength of $3T$, $\Delta E =
5.283 \times 10^{-7} eV$, and $\frac{n_-}{n_+} \approx (1 - 2.25 \times 10^{-5})$. This relatively tiny fraction of
excess spin polarization is the source of the NMR signal. Luckily, there are $3.3428 \times 10^{23}$ protons in a gram
of water, resulting in $7.5 \times 10^{18}$ aligned spins per gram under the previously stated conditions. Since living
things tend to contain mostly water, the proposal of MRI is still promising.

\begin{equation}\label{eq:boltzmann}
    \frac{n_-}{n_+} = \exp(-\frac{\Delta E}{k T}) = \exp(-\frac{\gamma \hbar B_0}{k T})
\end{equation}

In a large population of spins, the net magnetic dipole moment per unit volume is termed $\bvec{M}$. In equilibrium, it
is the product of the volumetric spin density $N$, the magnitude of a single spin dipole moment $\mu$, and the excess
fraction of aligned spins. It points in the same direction as $\bvec{B_0}$ and has magnitude $M_0$. Using the first two
terms of a taylor series expansion of the Boltzmann distribution, we can approximate $M_0$ as eq. \ref{eq:M}.

\begin{equation}\label{eq:M}
    M_0 = N \cdot \mu \cdot (1-\exp(-\frac{\Delta E}{k T})) \approx \frac{N \gamma^2 \hbar^2 B_0}{2 k T}
\end{equation}

\subsection{Spin Dynamics}
In equilibrium, $\bvec{M}$ comes to point in the direction $\bvec{B_0}$ with magnitude $M_0$. But the next step will be
to tip $\bvec{M}$ off of the $z$ axis so that it has a component in the $x$-$y$ plane. The observed behavior will then
be time varying.

\subsubsection{Precession}
A single magnetic dipole $\bvec{\mu}$ with mutually aligned angular momentum $\bvec{S}$ placed in an external magnetic
field $\bvec{B}$ will experience a torque $\bvec{\mu} \times \bvec{B}$. Multiplying this torque by $\gamma$ gives an
expression for the time rate of change of $\bvec{\mu}$, eq. \ref{eq:dipole_precession}. Eq. \ref{eq:dipole_precession}
shows $\bvec{\mu}$ moving in a direction perpendicular to both itself and $\bvec{B}$, i.e. precessing about $\bvec{B}$.
The frequency of this precession is $\omega_L$ in eq. \ref{eq:precession_freq}.

\begin{equation}\label{eq:dipole_precession}
    \frac{d \bvec{\mu}}{dt} = \bvec{\mu} \times \gamma \bvec{B}
\end{equation}

\begin{equation}\label{eq:precession_freq}
    \omega_L = \gamma \cdot B
\end{equation}

A population of dipole moments precessing in synchrony gives a net magnetization $\bvec{M}$ that also precesses at
$\omega_L$.

\subsubsection{Longitudinal Relaxation}
Define the component of $\bvec{M}$ that is parallel to $\bvec{B_0}$ as $\bvec{M_z}$. In equilibrium $|\bvec{M_z}| =
M_0$, but immediately following the tipping of $\bvec{M}$ into the $x$-$y$ plane by an angle $\alpha$ at time $t=0$,
$\bvec{M_z}$ is reduced to a value shown in eq. \ref{eq:mz_postflip}.

\begin{equation}\label{eq:mz_postflip}
    \bvec{M_z}(t=0+) = \cos(\alpha) \cdot \bvec{M_z}(0-)
\end{equation}

$\bvec{M_z}$ then begins to exponentially recover to its equilibrium magnitude of $M_0$. The time constant associated
with this longitudinal recovery is termed $T_1$. $T_1$ is dependent on the tissue or material being imaged, but also has
a positive dependence on $B_0$ field strength.

\begin{equation}\label{eq:t1_decay}
    \bvec{M_{z}}(t) = \uvec{k} M_0 + (\bvec{M_{z}}(0+) - \uvec{k} M_0) \cdot \exp(-\frac{t}{T_1})
\end{equation}

\subsubsection{Transverse Relaxation}
Define the component of $\bvec{M}$ that is perpendicular to $\bvec{B_0}$ as $\bvec{M_{xy}}$. In equilibrium,
$\bvec{M_{xy}} = 0$.  Immediately following the tipping of $\bvec{M}$ into the $x$-$y$ plane by an angle $\alpha$ at
time $t=0$, $\bvec{M_{xy}}$ is as shown in eq. \ref{eq:mxy_postflip}. Individual spins begin to dephase as soon as they
are tipped into the $x$-$y$ plane, and so the net transverse magnetization $\bvec{M_{xy}}$ experiences exponential
decay, as shown in eq. \ref{eq:t2_decay}. The time constant associated with this transverse decay is termed $T_2$, and
is a property of the tissue or material being imaged.

\begin{equation}\label{eq:mxy_postflip}
    \bvec{M_{xy}}(t=0+) = \uvec{i}\sin(\alpha) \cdot |\bvec{M_z}(0-)|
\end{equation}

\begin{equation}\label{eq:t2_decay}
    \bvec{M_{xy}}(t) = \bvec{M_{xy}}(0+) \cdot \exp(-\frac{t}{T_2})
\end{equation}

\subsection{Bloch Equation}
Assembled together, the spin dynamics described above form the Bloch equation, shown in eq. \ref{eq:bloch}. The complete
Bloch equation describes the behavior of spins in a generalized external magnetic field $\bvec{B}$ that is the sum of
the main field $B_0$, the RF field $B_1$, and the linearly varying gradient fields $G$. 

\begin{equation}\label{eq:bloch}
    \frac{d \bvec{M}}{dt} = \bvec{M} \times \gamma \bvec{B} - \frac{M_x \uvec{i} + M_y \uvec{j}}{T_2} - \frac{(M_z - M_0)
    \uvec{k}}{T_1}
\end{equation}

\subsection{RF Excitation}
In the previous section, we covered what happens when $\bvec{B} = B_0 \uvec{k}$; the steady state solution to the Bloch
equation is $\bvec{M} = M_0 \uvec{k}$, where $M_0$ is as defined in eq. \ref{eq:M}.  Now consider the case where
$\bvec{B}$ is as in eq. \ref{eq:B_rot}. A transverse component rotating at a frequncy $\omega_R$ and with time varying
amplitude $B_1(t)$ has been added. 

\begin{equation}\label{eq:B_rot}
    \bvec{B} = B_0 \uvec{k} + B_1(t) \cdot (\cos(\omega_R t) \uvec{i} - \sin(\omega_R t)\uvec{j})
\end{equation}

\section{Signal Equation}

The NMR signal arises from the precessing transverse component of the magnetization vector. As we begin to focus solely
on $\bvec{M_{xy}}$, I will follow the convention used by Nishimura \cite{nishimura} and define a new variable $M$ that
represents the transverse magnetization as a function of location and time with single complex number.

\begin{equation}\label{eq:M_complex}
    M(\bvec{r},t) \equiv |\bvec{M_x}| + j |\bvec{M_y}|
\end{equation}

\subsection{Signal Detection Through Faraday Induction}

The wire loop antenna is the most commonly used receive element in clinical MRI. It works by directly coupling to the
transverse magnetization of the sample under test. The precessing magnetization produces a time varying magnetic flux
piercing the surface defined by the loop, which induces a voltage $\epsilon$ around the loop through Faraday induction.

\begin{equation}\label{eq:faraday_induction}
    \epsilon = - \frac{d \Phi_B}{dt} = -\frac{d}{dt} \iint_A B(\bvec{r},t) dA
\end{equation}

A loop antenna has spatially varying sensitivity to spins.  If a unit current through the loop produces a field
$\bvec{B_1}$ at location $\bvec{r}$ in the sample, then magnetization $\bvec{M}$ at that location produces a flux of
$\bvec{B_1} \cdot \bvec{M}$ through the loop.  \cite{Hoult1979}. Citing linearity, we can find an expression for the
total voltage induced around the loop by summing the individual contributions from every location in the sample volume.

\begin{equation}\label{eq:reciprocity}
    \epsilon = -\frac{d}{dt} \iiint_V \bvec{B_1}(\bvec{r}) \cdot \bvec{M}(\bvec{r}) d\bvec{r}
\end{equation}

The voltage around the loop depends on a volume integral over the entire sample volume.

\subsection{Gradient Fields}

Spatial encoding in traditional MRI is achieved by applying linearly varying gradient fields on top of the main field,
as shown in eq. \ref{eq:gradients}. Just like $\bvec{B_0}$, $\bvec{G}$ points in the $\uvec{k}$ direction. Unlike
$\bvec{B_0}$, $\bvec{G}$ varies as a function of space and time.

\begin{equation}\label{eq:gradients}
    \bvec{B} = (B_0 + G(\bvec{r},t))\uvec{k}
\end{equation}

After an initial flip resulting in a spatial magnetization distribution $M(\bvec{r})$, spins begin precess under the
influence of $G$, as described in \ref{eq:phase_enc}. After a time $t$, spins at a location $\bvec{r}$ have accrued
excess phase in proportion to the time integral of $G(\bvec{r},t)$.

\begin{equation}\label{eq:phase_enc}
    M(\bvec{r},t) = M(\bvec{r,t=0}) e^{-j \gamma B_0 t} exp(-j \gamma \int_0^t G(\bvec{r},\tau) d \tau)
\end{equation}

This phase based encoding of spatial information is the essence of traditional MRI.

\subsection{The Fourier Transform}
The 1D Fourier transform breaks down a function of a single variable into its individual frequency components. Its form
is shown eq. \ref{eq:fourier_transform}
\begin{equation}\label{eq:fourier_transform}
    F(k_x) = \int_{-\infty}^{\infty} f(x)e^{-j2\pi k_x x} dx
\end{equation}





\section{Imaging Methods}
\subsection{RF Excitation}
\subsection{Linear Gradient Fields}
\subsection{Imaging with the 2DFT}

\section{Noise in MRI}
